Enforced Invariant Confluence

### 2018-09-19 doc/paper/sections/segmented_invariant_confluence.tex
Remove optimizations + limitations of segmentation
This commit addresses two pieces of reviewer feedback.

From reviewer 12:

> The optimizations are simply vaguely discussed in Section 6.4.

I completeley removed the vague paragraph on optimizations. It is vague,
not super important, and the paper is a bit long.

Also from reviewer 12:

> Regarding segmented invariant confluence, it does not seem easy to
> find good "quality" segments, which relates to how usable Section 6
> could be. The paper may include some discussions on how segments are
> constructed.

We already had a paragraph saying

\subsection{Discussion}
There are a few things worth noting about segmented
\invariantconfluence{}, its system model, and its decision procedure.
%
First, \invariantconfluence{} is a very coarse-grained property. If an object
is \invariantconfluent{}, then we can replicate it with no coordination. If it
is not \invariantconfluent{}, then we have no guarantees. There's no
in-between.  Segmented \invariantconfluence{}, on the other hand, is a much
more fine-grained property that can be applied to applications with varying
degrees of complexity. Segmented \invariantconfluence{} provides guarantees to
complex applications that require a large number of segments and to simple
applications with a smaller number of segments, whereas \invariantconfluence{}
only provides guarantees to applications that can be segmented into a single
segment.

@@

Second, we can integrate a couple of optimizations into our system model to
further reduce the amount of coordination it requires. For example, servers can
buffer transactions that require global coordination, executing an entire batch
of these transactions during a single round of global coordination.

Third, a segmented \invariantconfluence{} decision procedure can also leverage
\thmref{LatticeProperty} in addition to
\algoref{ArbitraryStartInteractiveDecisionProcedure}. If an object $O$ meets
criteria (1) - (3), then it is \sticonfluent{s}{T}{I} for every state $s \in
I$.

Fourth, while a segmented \invariantconfluence{} decision procedure can help
decide whether or not an object is segmented \invariantconfluent{}, it cannot
currently help construct a segmentation. In the future, we plan to explore
ways by which we can automatically suggest segmentations to the application
designer.

>>>>

\subsection{Discussion and Limitations}
There are a couple of things worth noting about segmented
\invariantconfluence{}, its system model, and its decision procedure.
%
First, \invariantconfluence{} is a very coarse-grained property. If an object
is \invariantconfluent{}, then we can replicate it with no coordination. If it
is not \invariantconfluent{}, then we have no guarantees. There's no
in-between.  Segmented \invariantconfluence{}, on the other hand, is a much
more fine-grained property that can be applied to applications with varying
degrees of complexity. Segmented \invariantconfluence{} provides guarantees to
complex applications that require a large number of segments and to simple
applications with a smaller number of segments, whereas \invariantconfluence{}
only provides guarantees to applications that can be segmented into a single
segment.

@@

% Second, we can integrate a couple of optimizations into our system model to
% further reduce the amount of coordination it requires. For example, servers can
% buffer transactions that require global coordination, executing an entire batch
% of these transactions during a single round of global coordination.
%
% Third, a segmented \invariantconfluence{} decision procedure can also leverage
% \thmref{LatticeProperty} in addition to
% \algoref{ArbitraryStartInteractiveDecisionProcedure}. If an object $O$ meets
% criteria (1) - (3), then it is \sticonfluent{s}{T}{I} for every state $s \in
% I$.

Second, while a segmented \invariantconfluence{} decision procedure can help
decide whether or not an object is segmented \invariantconfluent{}, it cannot
currently help construct a segmentation. It is the responsibility of the
programmer to think of a segmentation that is amenable to segmented
\invariantconfluence{}, and this can be an onerous process. In the future, we
plan to explore ways by which we can automatically suggest segmentations to the
application designer to ease this process.
